---
title: "Weight of Fish"
author: "David Santana"
date: "11/1/23"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight
find the best model using 2 variables to predict perch weight,
and compare this to the best overall model.


## Perch

```{r}
perch = filter(fish, Species == 'Perch')
```

### Best Two regressor model

```{r}
modelPerch <- regsubsets(Weight ~ Length1 + Length2 + Length3 + Height+ Width, data=perch, nvmax = )
summary(modelPerch)
```


### Best Two progressor model

```{r}
bestPerch = lm(Weight ~ Height + Width, data = perch)
summary(bestPerch)
```



### best 2-variable equation

Weight = -536 + 74.77*Height + 69.62*Width


## Pike

```{r}
pike = filter(fish, Species == 'Pike')
```


### Best Two progessor model
```{r}
modelpike <- regsubsets(Weight ~ Length1 + Length2 + Length3 + Height+ Width, data=pike, nvmax = )
summary(modelpike)
```


### Best 2-variable prediction is

```{r}
best2Pike = lm(Weight ~ Length1 + Length3, data = pike)
summary(best2Pike)
```
### Best 2-variable equation
Weight = -1675.79 + 0.04336*Length1 + 0.00482*Length3



## Roach

```{r}
Roach = filter(fish, Species == 'Roach')
```

## Best Two regressor model

```{r}
modelRoach <- regsubsets(Weight ~ Length1 + Length2 + Length3 + Height+ Width ,data=Roach, nvmax = )
summary(modelRoach)
```

### Best 2-variable prediction is

```{r}
best2Roach = lm(Weight ~ Length3 + Width, data = pike)
summary(best2Roach)
```

## Best 2-variable equation
Weight =  -1599.742 + 2.46e-05*Length3 + 0.917 *Width


## Final Summary Statements
The best model for Perch was Height + Width, for Pike it was Length1 + Length3, and for Roach it was Length3 + Width. The Adjusted R-Squared for each one was Perch is R-squared:   0.94, for Pike it was R-squared:  0.9649 , for Roach it was R-squared:  0.9526.